The Concurrent Calculi Formalisation Benchmark\thanks{The work is partially supported by EPSRC EP/T006544/2.}

### 2024-04-15 short-paper/short-paper.tex
Add some more explanation of the target audiences.

To achieve design goal~\ref{item:goal-comperison-accessibility}, our challenges explore the three aspects
(linearity, scope extrusion, coinduction) independently, so that they
may be solved individually and in any order; each challenge is small and easily understandable with basic knowledge of
textbook concurrency theory, process calculi, and type theory.  The
process calculi used in the challenges focus on the features that
we want to emphasise, and omit all constructs that would complicate the mechanisation without bringing
tangible insights.  The minimality and uniformity of the
calculi also allows us to target design goal~\ref{item:goal-tutorials}.
Aligned with design goal~\ref{item:goal-reusability}, our challenges concern the fundamental meta-theory of process calculi.
Our challenges centre around well-established results, showcasing proof techniques that can be leveraged in many applications (as we will further discuss in \cref{sec:going-beyond}).

>>>>

To achieve design goal~\ref{item:goal-comperison-accessibility}, our challenges explore the three aspects
(linearity, scope extrusion, coinduction) independently, so that they
may be solved individually and in any order; each challenge is small and easily understandable with basic knowledge of
textbook concurrency theory, process calculi, and type theory.
For mechanisation experts, our challenges should thus be accessible even without any prior understanding of process calculi.
The process calculi used in the challenges focus on the features that we want to emphasise, and omit all constructs that would complicate the mechanisation without bringing tangible insights.
For concurrency experts venturing into mechanisation, our challenges thus serve as good first steps.
The minimality and uniformity of the calculi also allows us to target design goal~\ref{item:goal-tutorials}.
For experts in both mechanisation and concurrency, our challenges serve as a framework in which to consider and share best practices and tutorials.
Aligned with design goal~\ref{item:goal-reusability}, our challenges concern the fundamental meta-theory of process calculi.
Our challenges centre around well-established results, showcasing proof techniques that can be leveraged in many applications (as we will further discuss in \cref{sec:going-beyond}).
